---
title: "ADA"
output: html_document
date: "2022-11-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("pacman")
library(pacman)
p_load(dplyr,foreign)
pacman::p_load(dplyr, ggplot2, car, odds.n.ends,readr, tidyverse, broom,lmtest,table1)
```

#Import the data and view all the column names
```{r}
BRFSS_a <- read.xport("/Users/yuansui/Desktop/LLCP2021.XPT ")
colnames(BRFSS_a)
```
#select several columns related to this analysis and make sure they were correctly selected
```{r}
BRFSSVar <- c("SEQNO","X_RACE","X_AGE65YR","CVDSTRK3","X_FRTLT1A","MARITAL","EDUCA","SEXVAR","X_BMI5CAT")
BRFSS_b <- BRFSS_a[BRFSSVar]
colnames(BRFSS_b)
```
#creating the dataset for analysis by including people aged 65 or older and exclude people with missing IV/DV/covariate variables
```{r}

BRFSS_c <- subset(BRFSS_b,X_AGE65YR==2) #target population:people above 65
BRFSS_d <- subset(BRFSS_c,CVDSTRK3 %in% c(1,2) & X_FRTLT1A %in% c(1,2)) #non-missing IV and DV
BRFSS_e <- subset(BRFSS_d, 
                    MARITAL %in% c(1,2,3,4,5,6) & 
                    X_RACE %in% c(1,2,3,4,5,6,7,8) &
                    EDUCA %in% c(1,2,3,4,5,6) &
                    SEXVAR %in% c(1,2) &
                    X_BMI5CAT %in% c(1,2,3,4)) #non-missing marital status, race,education,sex,BMI


#take a look at IV and DV
table(BRFSS_e$CVDSTRK3,BRFSS_e$X_FRTLT1A)
```

#data management and making table 1
```{r}
# making all categorical variables factors, finished re-coding of marital status
BRFSS_e<-BRFSS_e %>% 
  mutate(Fruit = case_when(X_FRTLT1A == 2 ~ 1, X_FRTLT1A == 1 ~ 0), Recode_marital = case_when(MARITAL %in% c(2,3,4,5,6) ~ 0, MARITAL %in% c(1) ~ 1)) %>% 
  mutate(Fruit = factor(Fruit, levels = c(0, 1), labels = c("At least once a  day", "Less than once a day"))) %>% 
  mutate(Stroke=case_when(CVDSTRK3==2~0,CVDSTRK3==1~1)) %>% 
  mutate(Stroke = factor(Stroke, levels = c(0, 1), labels = c("No Stroke History", "With Stroke History"))) %>% 
  mutate(RACE = factor(X_RACE, levels = c(1,2,3,4,5,6,7,8),labels = c("White only, non-Hispanic","Black only, non-Hispanic","American Indian or Alaskan Native only, Non-Hispanic","Asian only, non-Hispanic","Native Hawaiian or other Pacific Islander only, Non-Hispanic","Other race only, non-Hispanic","Multiracial, non-Hispanic","Hispanic"))) %>% 
  mutate(EDU = factor(EDUCA, levels = c(1,2,3,4,5,6),labels = c("Never attended school or only kindergarten","Grades 1 through 8 (Elementary)","Grades 9 through 11 (Some high school)","Grade 12 or GED (High school graduate)","College 1 year to 3 years (Some college or
      technical school)","College 4 years or more (College graduate)"))) %>% 
  mutate(SEX = factor(SEXVAR, levels = c(1,2),labels = c("Male","Female"))) %>% 
  mutate(Marital_Status= factor(MARITAL, levels = c(1,2,3,4,5,6),labels = c("Married","Divorced","Widowed","Separated","Never married","A member of an unmarried couple"))) %>% 
  mutate(BMI = factor(X_BMI5CAT, levels = c(1,2,3,4),labels = c("Underweight","Normal Weight","Overweight","Obese"))) %>% 
  mutate(Recode_married = factor(Recode_marital, levels = c(1,0),labels = c("Married","Other")))


#making table 1
label(BRFSS_e$EDU)<-"Education"
label(BRFSS_e$Marital_Status)<-"Marital Status"
table1(~SEX + EDU + RACE + Marital_Status + BMI|Stroke, BRFSS_e)

```

#having the base model and doing lrtest for potential effect modification 
```{r}
library(MASS)
#make a table with IV and DV
Table1 = table(BRFSS_e$Stroke,BRFSS_e$Fruit)
Table1
chisq.test(Table1)


#model1 is calculating the unadjusted OR and 95%CI
model1 <- glm(Fruit ~ Stroke,
               data = BRFSS_e,
               family = binomial,
              )
exp(confint.default(model1)[2,])
exp(coefficients(model1))
summary(model1)

#model2 is calculating the adjusted OR and 95%CI by adjusting education,race,sex,BMI,and marital status
model2 <- glm(Fruit ~ Stroke + EDU + RACE + SEX +BMI +Marital_Status,
               data = BRFSS_e,
               family = binomial,
              )
exp(confint.default(model2)[2,])
exp(coefficients(model2))
summary(model2)

#testing the effect modification by marital status with LR test,  the hypothesis was that marital status modifies the association between having a stroke history and having fruit less than one time a day
#re-coded marital status was used because married stroke survivors might receive better and more stable care from their partners
aa <- glm(Fruit ~ Stroke + Recode_marital,
               data = BRFSS_e,
               family = binomial,
              )
bb <- glm(Fruit ~ Stroke + Recode_marital +Stroke*Recode_marital ,
               data = BRFSS_e,
               family = binomial,
              )

lrtest(aa,bb) #The interaction term is significant via the LR test, so the next step is to run models stratified by Recode_marital

```

#making datasets for subgroup analysis, stratified by Recode_marital(married and other)
```{r}
BRFSS_f <- BRFSS_e %>% 
  drop_na()
BRFSS_m_0 <-  subset(BRFSS_e,Recode_marital==0) 
BRFSS_m_1 <-  subset(BRFSS_e,Recode_marital==1) 

#model3 is calculating the adjusted OR and 95%CI by adjusting education,race,sex,and BMI among 'other relations'
model3 <- glm(Fruit ~ Stroke + EDU + RACE + SEX +BMI,
               data = BRFSS_m_0,
               family = binomial,
              )
exp(confint.default(model3)[2,])
exp(coefficients(model3))
summary(model3)

#model4 is calculating the adjusted OR and 95%CI by adjusting education,race,sex,and BMI among 'married people'
model4 <- glm(Fruit ~ Stroke + EDU + RACE + SEX +BMI,
               data = BRFSS_m_1,
               family = binomial,
              )
exp(confint.default(model4)[2,])
exp(coefficients(model4))
summary(model4)
```




